Quick, Draw! Image Classification

### 2018-12-07 report/draft.tex
updating section 2.4

We have generated the following hypotheses based on theoretical
expectations:

@@

TODO: more context would be helpful here, maybe some citations

@@

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[scale=0.75]{fig2}
    \end{center}
  \caption{Fully Connected Neural Network Architecture}
  \label{fig:fcnn}
  \end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[scale=0.5]{fig3}
    \end{center}
  \caption{CNN Architecture}
  \label{fig:cnnArch}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[scale=0.5]{fig4}
  \end{center}
  \caption{CNN Architecture with Reduced Parameters}
  \label{fig:cnnArchPool}
\end{figure}

@@

>>>>

We have generated the following hypotheses based on theoretical
expectations expressed in the literature \cite{Goodfellow-et-al-2016,
  DeepLear51:online}. Performance is effected by both the model and
data \cite{DeepLear51:online} so our hypotheses pertain to both effects.

@@

@@

\subsection{Modeling Strategy}

We provide our modeling strategy as it relates to the exploration of
our stated hypotheses.

\subsubsection{Baseline image classification using humans}

Two group members completed a Human Intelligence Task by manually
classifying images into one of our ten defined categories. This
approach helped us get a benchmark which we could use to
define ``reasonable accuracy''.

\subsubsection{$H1_a$: Fully connected neural network will struggle
  to get reasonable accuracy}

In order to perform this experiment, we built a fully connected neural network
using Tensorflow. Our train:test split was chosen to be 80:20, an industry
standard. Our initial objective was to build a model that overfit our given
dataset, with the idea that once our model is complex enough to overfit the
training data, we could regularize it in order to achieve a more optimal fit.
The fully connected neural network had 20,067 parameters.

After experimenting with various architectures, we narrowed down to a 3 layer
model as specified in Figure \ref{fig:fcnn} in the Appendix. The model was
run on a machine with 13 GB of RAM, Intel Xeon CPU 2.3 GHz (1 core, 2
threads), 1xTesla K80 GPU having 2496 CUDA cores with 12 GB GDDR5 VRAM.

\subsubsection{$H2_a$ CNN should perform better than fully connected neural
  network}

As for the CNN, we started off with the same approach with attempting
to overfit the model using convolution operations and a fully connected
layer with an objective to categorise 10 categories, softmax was chosen
as the activation function for the final layer, while every other neuron
had ReLU as the activation function owing to ReLU’s faster convergence. See
Figure \ref{fig:cnnArch} for a representation of this first CNN model.

The number of parameters is much greater than the number of observations
used to train the model resulting in overfitting. In order to reduce the
number of parameters, we incorporated Pooling (Max Pooling) post each
convolution operation extracting only the most significant features
resulting in reduction of the volume of the convolutional output, giving
the model a smaller memory footprint as well as a smaller number of
trainable parameters. Figure \ref{fig:cnnArchPool} has a representation of this
second CNN model. We employ strategies to reduce overfitting related to
dropouts and stride in addition to adding more training data.

@@

@@

@@

@@

\begin{figure}[h!]
  \begin{center}
    \includegraphics[scale=0.75]{fig2}
    \end{center}
  \caption{Fully Connected Neural Network Architecture}
  \label{fig:fcnn}
\end{figure}

\begin{figure}[h!]
  \begin{center}
    \includegraphics[scale=0.5]{fig3}
    \end{center}
  \caption{(CNN Model 1) Loss Function: Categorical Cross Entropy, Optimizer:
    Adam, Trainable Parameters: 320,890}
  \label{fig:cnnArch}
\end{figure}

\begin{figure}[h!]
  \begin{center}
    \includegraphics[scale=0.5]{fig4}
  \end{center}
  \caption{(CNN Model 2) Loss Function: Categorical Cross Entropy, Optimizer:
    Adam, Trainable Parameters: 19,322}
  \label{fig:cnnArchPool}
\end{figure}
